### 2021-06-01 paper/NIHGrant.tex
minor edits

To reconstruct cognitive representations from subject responses,
we will generate a classification spectrogram by taking the difference
between a spectrogram generated from the positive labels (the ``yes'' responses)
and a spectrogram generated from the negative labels (the ``no'' responses)
(\autoref{fig:experiment}).
Such reconstructed representations are the best least-squares fit to the behavioral data
\cite{gosselinSuperstitiousPerceptionsReveal2003}.
We theorize that the classification spectrogram is used as a template vector
against which stimuli are compared in a linear matching model of response generation.

>>>>

We will reconstruct cognitive representations of tinnitus from the data
by taking the least-squares fit to the behavioral data
(\autoref{fig:experiment}).
This is equivalent to interpreting the cognitive representation
as a ``classification spectrogram''
generated by subtracting the average of the negative trials from the average of the positive trials
\cite{gosselinSuperstitiousPerceptionsReveal2003}.
We theorize that in the underlying transductive cognitive process,
that the classification spectrogram is used as a template vector
against which stimuli are compared in a linear matching model of response generation.
While we acknowledge that this reconstruction approach is inefficient,
requiring many samples to acquire a coherent reconstruction,
it is well-studied in the literature
and will serve as a baseline against which our efficient reconstruction
algorithm in Aim \#2 will be compared.
